---
title: "Regression Model"
author: "Siti Asuroh"
date: "13 November 2018"
output: html_document
---
## Libraries and Setup
We'll set-up caching for this notebook given how computationally expensive some of the code we will write can get.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Programming with "data" Dataset
First make sure the data We'll like to work with is also in Our current directory, and use the `read.csv()` to read our csv file into our global environment. Then, delete the first column in the data. And then, name the columns.
The next step is to check the correlation of crime_rate and percent_m.  
```{r}
data<-read.csv("data_input/crime.csv")
data<-data[,-1]
names(data) <- c("percent_m", "is_south", "mean_education", "police_exp60", "police_exp59", "labour_participation", "m_per1000f", "state_pop", "nonwhites_per1000", "unemploy_m24", "unemploy_m39", "gdp", "inequality", "prob_prison", "time_prison", "crime_rate")
cor(data$crime_rate,data$percent_m)
```

We will need to use `install.packages()` to install any packages that are not already downloaded onto Our machine. And then, load the package into Our workspace using the `library()` function. The next step is to check the correlation of all variable :
```{r}
#install.packages("GGally"), krn gak ada
#install.packages("ggcorrplot")
#ggcorrplot(cor(data))
library(GGally)
ggcorr(data)
```
#Building the Regression Model with all variables
```{r}
Model1<-lm(crime_rate~.,data)
summary(Model1)
```
#Find the Best Model by Stepwise (Backward, Forward, Both)
```{r}
step(Model1,direction="backward")
```
#The best model of the Backward Method is taken from the smallest AIC value.
```{r}
Model2<-lm(formula = crime_rate ~ percent_m + mean_education + police_exp60 + 
    m_per1000f + unemploy_m24 + unemploy_m39 + inequality + prob_prison, 
    data = data)
summary(Model2)
```
#If the model has been obtained, then check Multicollinearity
```{r}
library(car)
vif(Model2)
```
Because all of the VIF values are <10 all, then the Multicollinearity assumption is fulfilled. And now, check normality by Histogram.

```{r}
hist(residuals(Model2))
```
#because it forms a bell curve, it can be concluded that it is Normal distribution.
And now, We will to plot the Residual for the Heteroscedasticity Test
```{r}
plot(data$crime_rate,residuals(Model2))
```
#When the plot does not form a pattern, the assumption of the Heteroscedasticity test is fulfilled

Interpretation:
1. The Model formed has an Adjusted R square Value of 0.7444, and all Assumption        Tests have been fulfilled.
2. The Model formed is y = -6426.101 + 9.332percent_m + 18.012mean_education +                                  10.265police_exp60 + 2.234m_per1000f -6.087 unemploy_m24                             +18.735unemploy_m39+6.133inequality -3796.032prob_prison                  




